---
output: md_document
---

# Links

```{r include=FALSE}
knitr::opts_chunk$set(comment = NULL)
```

```{r introCode, echo=FALSE, message=FALSE, warning=FALSE}
library("tidyverse")
library("kableExtra")
df_raw <- read_csv("data.csv")
df <- df_raw |> 
   transmute(title = paste0("[", title, "](", url, ")"), category)

```

The repository consists of a dataset with curated links to great material. There is a total of `r NROW(df)` active links in the dataset. 

# Life

```{r linksLife, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "life") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```


# Work

```{r linksWork, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "work") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# Food

```{r linksFood, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "food") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# Science

## Biology

```{r linksBiology, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "biology") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## Physics

```{r linksPhysics, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "physics") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## Psychology

```{r linksPsychology, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "psychology") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# Economics

```{r linksEconomics, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "economics") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# Climate

```{r linksClimate, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "climate") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# Business

```{r linksBusiness, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "business") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# Programming

```{r linksProgramming, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "programming") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# Privacy

```{r linksPrivacy, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "privacy") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# Ethics

```{r linksEthics, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "ethics") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# Technology

```{r linksTechnology, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "technology") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# Reasoning

```{r linksReasoning, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "reasoning") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```


# Culture

## Art

```{r linksArt, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "art") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## Books

```{r linksBooks, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "books") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## Movies

```{r linksMovies, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "movies") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## TV

```{r linksTV, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "tv") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## Music

```{r linksMusic, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "music") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## Games

```{r linksGames, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "games") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

### Chess

```{r linksChess, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "chess") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# Knowledge

```{r linksKnowledge, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "knowledge") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# Language

```{r linksLanguage, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "language") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## English

```{r linksEnglish, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "english") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# Travel

```{r linksTravel, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "travel") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# Countries

## Denmark

```{r linksDenmark, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "Denmark") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## Germany

```{r linksGermany, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "Germany") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## Russia

```{r linksRussia, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "Russia") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```


# Health

```{r linksHealth, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "health") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# Sport

```{r linksSport, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "sport") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# Transport

```{r linksTransport, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "transport") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# Politics

```{r linksPolitics, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "politics") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# Design

```{r linksDesign, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "design") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```


# Essays

```{r linksEssays, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "essay") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```
