---
output: md_document
---

# Links

```{r include=FALSE}
knitr::opts_chunk$set(comment = NULL, echo = FALSE, message = FALSE, warning = FALSE, results = "asis")
```

```{r introCode, echo=FALSE, message=FALSE, warning=FALSE}
library("tidyverse")
library("kableExtra")
df_raw <- read_csv("data.csv")
df <- df_raw |> 
   transmute(title = paste0("[", title, "](", url, ")"), category)

```

The repository consists of a dataset with curated links to great material. There is a total of `r NROW(df)` active links in the dataset. 

# âœ¨ Life

```{r linksLife, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "life") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```


# ðŸ’¼ Work

```{r linksWork, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "work") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# ðŸ” Food

```{r linksFood, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "food") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# âš—ï¸Science

```{r linksScience, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "science") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## ðŸ§¬ Biology

```{r linksBiology, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "biology") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## ðŸŒ  Physics

```{r linksPhysics, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "physics") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## ðŸ§  Psychology

```{r linksPsychology, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "psychology") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# ðŸ“ Mathematics

```{r linksMathematics, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "mathematics") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```


# ðŸ’° Economics

```{r linksEconomics, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "economics") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# ðŸŒ Climate

```{r linksClimate, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "climate") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# ðŸŒ³ Nature

```{r linksNature, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "nature") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# ðŸ’¼ Business

```{r linksBusiness, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "business") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# ðŸ’» Programming

```{r linksProgramming, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "programming") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# ðŸ”’ Privacy

```{r linksPrivacy, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "privacy") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# âš–ï¸ Ethics

```{r linksEthics, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "ethics") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# ðŸŒ Technology

```{r linksTechnology, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "technology") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# ðŸ¤” Reasoning

```{r linksReasoning, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "reasoning") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# âœï¸ Writing

```{r linksWriting, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "writing") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## LaTeX

```{r linksLaTeX, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "latex") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# Culture

## ðŸŽ¨ Art

```{r linksArt, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "art") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## ðŸ“š Books

```{r linksBooks, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "books") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## ðŸŽ¬ Movies

```{r linksMovies, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "movies") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## ðŸ“º TV

```{r linksTV, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "tv") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## ðŸŽµ Music

```{r linksMusic, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "music") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## ðŸŽ™ï¸ Podcasts

```{r linksPodcasts, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "podcast") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## ðŸŽ® Games

```{r linksGames, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "games") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

### â™Ÿï¸Chess

```{r linksChess, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "chess") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# ðŸŽ“ Knowledge

```{r linksKnowledge, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "knowledge") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# Language

```{r linksLanguage, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "language") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## English

```{r linksEnglish, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "english") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# âœˆï¸ Travel

```{r linksTravel, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "travel") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# Countries

## Denmark

```{r linksDenmark, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "Denmark") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## Azerbaijan

```{r linksAzerbaijan, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "Azerbaijan") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## United Kingdom

```{r linksUK, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "UK") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## Netherlands

```{r linksNetherlands, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "Netherlands") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## Germany

```{r linksGermany, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "Germany") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## Italy

```{r linksItaly, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "Italy") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)

```


## Nigeria

```{r linksNigeria, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "Nigeria") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)

```

## Russia

```{r linksRussia, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "Russia") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## Egypt

```{r linksEgypt, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "Egypt") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## Saudi Arabia

```{r linksSaudiArabia, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "SaudiArabia") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## United States

```{r linksUS, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "US") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## Japan

```{r linksJapan, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "Japan") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# ðŸ‘• Fashion

```{r linksFashion, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "fashion") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# âš•ï¸Health

```{r linksHealth, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "health") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# âš½ Sport

```{r linksSport, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "sport") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# ðŸš¦ Transport

```{r linksTransport, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "transport") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# ðŸ“œ Politics

```{r linksPolitics, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "politics") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# ðŸ“– History

```{r linksHistory, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "history") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# ðŸ“° Design

```{r linksDesign, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "design") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# ðŸ¢ Architecture

```{r linksArchitecture, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "architecture") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```


# âœ’ï¸ Essays

```{r linksEssays, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "essay") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```
