---
output: md_document
---

# Links

```{r include=FALSE}
knitr::opts_chunk$set(comment = NULL)
```

```{r introCode, echo=FALSE, message=FALSE, warning=FALSE}
library("tidyverse")
library("kableExtra")
df_raw <- read_csv("data.csv")
df <- df_raw |> 
   transmute(title = paste0("[", title, "](", url, ")"), category)

```

The repository consists of a dataset with curated links to great material. There is a total of `r NROW(df)` active links in the dataset. 

# TODO

- add categories:  "business" "climate" "design" "economics" "ethics" "food"  "news"  "politics" "privacy" "programming"  "reasoning" 

# Life

```{r linksLife, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "life") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```


# Work

```{r linksWork, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "work") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# Science

## Biology

```{r linksBiology, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "biology") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## Physics

```{r linksPhysics, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "physics") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## Psychology

```{r linksPsychology, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "psychology") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# Culture

## Art

```{r linksArt, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "art") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## Books

```{r linksBooks, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "books") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## Movies

```{r linksMovies, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "movies") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## TV

```{r linksTV, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "tv") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## Music

```{r linksMusic, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "music") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

## Games

```{r linksGames, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "games") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```


# Language

## English

```{r linksEnglish, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "english") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# Health

```{r linksHealth, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "health") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# Sport

```{r linksSport, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "sport") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# Transport

```{r linksTransport, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "transport") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```

# Essays

```{r linksEssays, echo=FALSE, message=FALSE, warning=FALSE}
df |> 
  filter(category == "essay") |> 
  pull(title) |> 
  pander::pandoc.list(add.end.of.list = FALSE)
```
